---
title: "SES6003 Assessment 3 - Super Netball"
author: "Shaun Lenehan"
date: "14/03/2022"
output: 
  html_document:
    code_folding: show
---

```{r setup, R.options=knitr::opts_chunk$set(warnings=FALSE, message=FALSE, fig.width=12, fig.height=8)}
```

## Aim of Analysis
The aim of the following analysis is to determine if teams that take more shots from ***Zone 2*** score more points than teams that do not.

## Step 1. Load The Required Packages

Before analysing the data the following packages will need to be loaded;

***here*** - constructs a path to the projects data file
 
***tidyverse*** - a set of packages designed to work in together, packages needed within tidyverse include ***dtplyr*** and ***ggplot2***
 
***knitr*** - provides a general purpose tool for generating reports

***plotly*** - creates interactive web graphics in conjunction with ggplot2
 
***viridis*** - colours graphs in a readable format for color blind individuals

```{r PackagesData}
# Load required packages
library(here)
library(tidyverse)
library(knitr)
library(plotly)
library(viridis)
library(flexdashboard)
```

## Step 2. Load the Data
Load the data by using the read.csv function and the ***here*** package.

```{r LoadData}
# Load in the data
Dataset3_Assessment3 <- read.csv(here("Data/Dataset3_Assessment3.csv"))
```

## Step 3. Run Summary Data
Determine the Min, Max, Mean, SD and Sum for each variable in the ***Statistic*** column.
```{r SummaryData}
#Create new dataframe
SummaryData_All <- Dataset3_Assessment3 %>%
group_by(Team, Statistic) %>%
summarise(Min = min(Total),
Max = max(Total),
Mean = mean(Total),
SD = sd(Total),
Sum = sum(Total))
```

## Step 4. Isolate Attempts from Zone 2 & Plot
Use the filter function to determine how many shots teams are taking from the 2-point zone.
```{r IsolateAttempts}
# Isolate with filter
SummaryData_attempt_from_zone2 <-
filter(SummaryData_All, Statistic == "attempt_from_zone2")
```

Plot Attempts on a boxplot to visualize/rank teams. 
```{r PlotAttempts}
# Boxplot Attempts with ggplot
PlotAttempts <- ggplot(SummaryData_attempt_from_zone2, aes(x = Statistic, y = Sum)) +
  geom_jitter(aes(colour = Team)) +
  scale_colour_viridis_d() +
  geom_boxplot(alpha = 0.3) +
  xlab("Attempts from Zone 2") +
  ylab("Sum of Shots Over Season") +
  ggtitle("Figure 1")+
  theme_classic()

# Make the PlotAttempts interactive
ggplotly(PlotAttempts)
```

Figure 1. shows a large variability in 2-point shots taken by teams. The Giants (211) 2X more than the Sunshine Coast (91). 

## Step 5. Isolate and Plot Points
By plotting points we can now get a idea of whether or not taking two points shots results in more total points. 
```{r IsolatePoints}
# Isolate with filter
SummaryData_Points <-
filter(SummaryData_All, Statistic == "points")
```

```{r PlotPoints}
# Boxplot Points with ggplot
PlotPoints <- ggplot(SummaryData_Points, aes(x = Statistic, y = Sum)) +
  geom_jitter(aes(colour = Team)) +
  scale_colour_viridis_d() +
  geom_boxplot(alpha = 0.3) +
  xlab("Points") +
  ylab("Sum of Points Over Season") +
  ggtitle("Figure 2")+
  theme_classic()

# Make the PlotPoints interactive
ggplotly(PlotPoints)
```

In Figure 2. you can see that over the season West Coast Fever scored the most points even though they took the 2nd least attempts from zone 2.

## Insights
Comparing Figure 1 & 2 suggest that attempting more shots from Zone 2 does not result in more points scored. The West Coast Fever are a good example of this (Attempts Rank - 7th / Points - 1st). This suggest that taking 2-point shots is not worth the effort!

One limitation of this study is that it does consider accuracy. West Coast Fever may take limited attempts but be very successful when they do. 

Completing Linear regression analysis would be the next step for this research. 